Jesse Dodge is a Senior Research Scientist at the Allen Institute for AI, on the AllenNLP team, working on natural language processing and machine learning. He is interested in the science of AI and AI for science, and he works on reproducibility and efficiency in AI research. He is involved in many parts of OLMo, a project to create fully open large language models, including creation of Dolma (a web-scale training dataset), Palmoa (an evaluation benchmark for language models), and incorporating ethical principles at every stage of the machine learning pipeline. His research has highlighted the growing computational cost of AI systems, including the environmental impact of AI and inequality in the research community. He has worked extensively on improving transparency in AI research, including open sourcing and documenting datasets, data governance, and measuring bias in data. He has also worked on developing efficient methods, including model compression and improving efficiency of training large language models. His PhD is from the Language Technologies Institute in the School of Computer Science at Carnegie Mellon University. He created the NLP Reproducibility Checklist, which has been used by five main NLP conferences, including EMNLP, NAACL, and ACL, totaling more than 10,000 submissions, he helped create the Responsible NLP Checklist which is used for submissions to ARR (replacing the Reproducibility Checklist), and was an organizer for the ML Reproducibility Challenge 2020-2022. His research has won awards including a Best Student Paper at NAACL 2015 and a ten-year Test of Time award at ACL 2022, and is regularly covered by the press, including by outlets like The New York Times, Nature, MIT Tech Review, Wired, and others.